Seasonality in governing dynamics at submesoscales in the Kuroshio Extension

### 2016-06-28 writeup/rocha_etal.tex
Small edits

\authors{Cesar et al. \altaffilmark{1}}
% Eric Brown,\altaffilmark{1,2} Rick Williams,\altaffilmark{3}
% John B. McDougall\altaffilmark{4}, and S. Visconti\altaffilmark{5}}

@@

\begin{abstract}
    Two new high-resolution numerical simulations with embedded tides suggest a
    strong modulation in the governing near-surface dynamics at submesoscales
    (roughly 10-100 km) in the Kuroshio Extension. Consistent with recent studies, deep late-Winter mixed layers
    are prone to baroclinic instabilities, and submesoscale turbulence
    prevails in late Winter/early Spring. Inertia-gravity waves are enhanced near
    the surface when the upper ocean is strongly stratified. Thus the summertime
    re-stratification weakens submesoscale turbulence and enhances intertia-gravity
     waves near the surface. In the Kuroshio Extension,
    inertia-gravity waves strongly dominate the submesoscale surface kinetic energy and
    sea-surface height variance in late Summer/early Fall.
\end{abstract}

@@

Our work adds to recent studies that presented modeling \cite{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean. Of course, our study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre; care must be taken to avoid overgeneralizing
these results.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.

>>>>

\authors{Cesar B. Rocha et al. \altaffilmark{1}}
% Eric Brown,\altaffilmark{1,2} Rick Williams,\altaffilmark{3}
% John B. McDougall\altaffilmark{4}, and S. Visconti\altaffilmark{5}}

@@

\begin{abstract}
    Two new high-resolution numerical simulations with embedded tides suggest a
    strong modulation in the governing near-surface dynamics at submesoscales
    (roughly 10-100 km) in the Kuroshio Extension. Consistent with recent studies, deep late-Winter mixed layers
    are prone to baroclinic instabilities, and submesoscale turbulence
    prevails in late Winter/early Spring. While summertime
    re-stratification weakens submesoscale turbulence, it also enhances intertia-gravity
     waves near the surface. In the Kuroshio Extension,
    inertia-gravity waves strongly dominate the submesoscale surface kinetic energy and
    sea-surface height variance in late Summer/early Fall.
\end{abstract}

@@

Our work adds to recent studies that presented modeling \cite{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean. Of course, this study on a single patch of ocean in the
vicinity of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre; care must be taken to avoid overgeneralizing
these results.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.
